### 2020-11-05 Thesis-Chapter1-Introduction.tex
Write going dark, golden age, and fallacies sections

The conversation over encryption is in a stalemate. Governments and law enforcement agencies frequently cite the need to
access encrypted data to perform their duties \cite{ministerial_2018} \cite{intl_2020} \cite{fbi_2020}. Human rights
groups and technical leaders counter that a weakened encryption environment would fatally compromise privacy and
security as we know it \cite{abelson_2015} \cite{eightythree_2017} \cite{ruiz_there_2018}. As the debate continues,
sides have become entrenched, and both sides have engaged in disingenuous attacks against their opponents.

>>>>

The conversation over encryption is in a stalemate. Governments and law enforcement agencies frequently cite the need to
access encrypted data to perform their duties \cite{ministerial_2018} \cite{intl_2020} \cite{comey_2014}. Human rights
groups and technical leaders counter that a weakened encryption environment would fatally compromise privacy and
security as we know it \cite{abelson_2015} \cite{eightythree_2017} \cite{ruiz_there_2018}. As the debate continues,
sides have become entrenched, and both sides have engaged in disingenuous attacks against their opponents.

### 2020-11-05 Thesis-Chapter3-PolicyMaking.tex
Write going dark, golden age, and fallacies sections

Cybersecurity law scholar Alan Rozenshtein argues for treating \ac{encryption} and \ac{EA} as a \ac{wicked-prob} at
length \cite{rozenshtein_wicked_2018}. He breaks the root issues down into three categories. First, that there is
disagreement on goals (or even basic premises). Sides can't agree whether things are ``going dark'' or we're in the
``golden age of surveillance'' or how much to value competing notions of security. Second, that information is
``uncertain and diffuse.'' There are insufficient statistics on encryption's effect on investigations, and though the
consensus is that we are not presently capable of acceptably secure \ac{EA}, that is not certain to always be the case,
especially as the area is under-researched. Third, that the problem cannot be definitively solved. Evolving values and
technology mean that the subject is always up for renegotiation.

>>>>

Cybersecurity law scholar Alan Rozenshtein argues for treating \ac{encryption} and \ac{EA} as a \ac{wicked-prob} at
length \cite{rozenshtein_wicked_2018}. He breaks the root issues down into three categories. First, that there is
disagreement on goals (or even basic premises). Sides can't agree whether things are ``going dark'' or we're in the
``golden age for surveillance'' or how much to value competing notions of security. Second, that information is
``uncertain and diffuse.'' There are insufficient statistics on encryption's effect on investigations, and though the
consensus is that we are not presently capable of acceptably secure \ac{EA}, that is not certain to always be the case,
especially as the area is under-researched. Third, that the problem cannot be definitively solved. Evolving values and
technology mean that the subject is always up for renegotiation.

### 2020-11-05 Thesis-Chapter4-Arguments.tex
Write going dark, golden age, and fallacies sections

\section{Contributing Factors}

As previously stated, it is \ac{encryption}'s dual role as enabler of radical privacy and cornerstone of security is at
the heart of the EA debate. Of course, there is only a conflict if one sees radical privacy as a bad thing. The right to
privacy is both a strongly held value and an enshrined legal principle, and many use privacy-based arguments to show
\ac{EA} as socially undesirable. The \ac{snowden} revelations \cite{landau_making_2013} only unveiled the scale of
privacy-eroding U.S. government surveillance enabled by technological changes, terrorism-motivated policies, and weak
oversight \cite{shamsi_2011}. Violations of privacy are concerning for those most vulnerable and for society at large.
For example, Saudi journalist Jamal Khashoggi's private communications were surveilled by the Saudi government before he
became a victim of politically motivated murder \cite{liebermann_2019}. At a societal level, presence of surveillance
alone changes behavior and chills free speech \cite{rogaway_moral_2015}, while government violations of the law degrade
institutional trust.

@@

See \myfig{fig-args-contrib} for the \ac{argmap} representing this section.

@@

% Actually fund initiatives to tackle these problems!
% pfefferkorn_2019
% keller_internet_2019

@@

@@

@@

@@

>>>>

\section{Contributing Factors}
\label{sed-arg-contrib}

\myfig{fig-args-contrib} maps the central arguments in the EA debate. As previously stated, it is \ac{encryption}'s dual
role as enabler of radical privacy and cornerstone of security is at the heart of the debate. Of course, there is only a
conflict if one sees radical privacy as a bad thing. The right to privacy is both a strongly held value and an enshrined
legal principle, and many use privacy-based arguments to show \ac{EA} as socially undesirable. The \ac{snowden}
revelations \cite{landau_making_2013} only unveiled the scale of privacy-eroding U.S. government surveillance enabled by
technological changes, terrorism-motivated policies, and weak oversight \cite{shamsi_2011}. Violations of privacy are
concerning for those most vulnerable and for society at large. For example, Saudi journalist Jamal Khashoggi's private
communications were surveilled by the Saudi government before he became a victim of politically motivated murder
\cite{liebermann_2019}. At a societal level, presence of surveillance alone changes behavior and chills free speech
\cite{rogaway_moral_2015}, while government violations of the law degrade institutional trust.

@@

@@

A significant portion of the disconnect between government and technical community representatives is disagreement over
whether law enforcement has \ii{too little} or \ii{too much} access to data. The argument for \ii{too little} is
well-represented by proponent former \ac{FBI} Director James Comey in a 2014 speech \cite{comey_2014} (though he did not
coin the phrase \cite{swire_encryption_2011}). The argument is represented in \myfig{fig-arg-going-dark}, also informed
by critiques \cite{rogaway_moral_2015}.

\begin{figure}[h]
  \centering\CaptionFontSize
  \includegraphics[width=\linewidth]{arguments/build/comprehensive.goingdark.pdf}
  \caption{A ``Going Dark'' Argument Map}
  \label{fig-arg-going-dark}
\end{figure}

The ``Going Dark'' argument goes that privacy and safety are both desirable goods, but they inherently conflict, and we
need balance. Individuals must give up some of their personal good of privacy to make room for the public good of
safety. Encryption tips the scales too far towards privacy, upsetting the balance of the status quo. \ac{EA} is needed
to restore the balance and enable law enforcement agencies to do their jobs and protect the public.

The argument has a few blind spots. Depicting privacy and safety as competing in a zero-sum tradeoff ignores all the
ways in which privacy directly enhances safety. Data privacy makes certain crimes more difficult, such as stalking or
identity theft. Privacy is also a public good to the extent that it precludes mass surveillance, an argument explored
more deeply in the ``Golden Age'' side of the argument.

Most importantly, the ``Going Dark'' argument hinges on encryption being responsible for failure of law enforcement
investigations. As described in \mysec{sed-arg-contrib}, there is a lack of data on the extent to which encryption is
itself to blame for failed cases. One can certainly understand the argument, but the lack of evidence is an issue. The
highest-profile case of \ac{the-cw2}, Apple vs. FBI, ended with the \ac{FBI} breaking into the phone but finding nothing
of value. Tellingly, each of Comey's examples in his 2014 speech were not cases where encryption inhibited
investigations, but where cases hypothetically \ii{could} have been inhibited if encryption was a factor
\cite{comey_2014}.

Citing lack of evidence only gets you so far, however. In most cases, it is impossible to know what would have happened
in an investigation unimpeded by strong encryption. This is part of why it is a \ac{wicked-prob}. Indeed, when the
encryption curtain is pulled back, there is often much to see. Unencrypted Facebook Messenger is has approximately 20\%
market share in active monthly users \cite{statista_2020} but accounts for 65\% of \ac{CSAM} reports
\cite{keller_internet_2019}, and European law enforcement's infiltration of encrypted messaging service Encrochat
exposed crime rings and led to a massive raids \cite{cox_2020}.

Aside from encryption entirely, a 2018 study found that law enforcement's primary challenges with digital evidence were
identifying service providers and getting the sought after data from them \cite{carter_2018}. This is in the context of
current legal frameworks and access capabilities. The report is fittingly titled ``Low-Hanging Fruit,'' and also lists
resource limitations and training needs among top priorities. Indeed, many current initiatives are underfunded. Major
anti-\ac{CSAM} legislation passed in 2008, but has been funded at only 50\% of authorized levels, the Justice Department
task force has produced only two of five biennial reports, and a senior executive position within the Justice Department
was never created \cite{keller_internet_2019}. Federal entities commissioned to improve communication between law
enforcement and industry as well as to train law enforcement on managing digital evidence are similarly underfunded
\cite{carter_2018}.

% Golden age

The argument for law enforcement having \ii{too much} access to data claims that instead of law enforcement ``Going
Dark,'' they are living in the ``Golden Age for Surveillance'' \cite{swire_encryption_2011}. This argument goes that
although encryption makes certain data completely unaccessible, technological change on the whole has given authorities
much more digital evidence than encryption has taken away. Paired with the dangers of mass surveillance, encryption is
a necessary defense, and any \ac{EA} implementation would compromise encryption's protection. The argument is mapped in
\myfig{fig-arg-golden-age}.

\begin{figure}[h]
  \centering\CaptionFontSize
  \includegraphics[width=\linewidth]{arguments/build/comprehensive.goldenage.pdf}
  \caption{A ``Golden Age for Surveillance'' Argument Map}
  \label{fig-arg-golden-age}
\end{figure}

The ``Golden Age'' argument revolves around surveillance, its undesirability, and technology's role in it. Cryptographer
Phillip Rogaway writes at length about the negative impacts of mass surveillance in his essay ``The Moral Character of
Cryptographic Work'' \cite{rogaway_moral_2015}. Rogaway argues that ``pervasive collection \ii{itself} chills
free-speech and threatens liberal democracy'' (emphasis his) through the way its mere existence affects the subject. He
argues that it is fundamentally a tool of power, and though I would add that power from the people created through
representative political process is valid power, clear abuses have undercut reasonable confidence in these institutions.

The next element is that technology has increased the government's surveillance powers. This can hardly be contested.
Going back to Comey's ``Going Dark'' examples once more, each case he cited was cracked by digital evidence that would
not have been available even twenty years ago \cite{comey_2014}. In response to the danger of mass surveillance and the
scale of modern surveillance capabilities, encryption is one of the only privacy-saving tools. (Opting out may be
possible for some, but is not a realistic option for society as a whole.)

While much stronger than the ``Going Dark'' argument, the ``Golden Age for Surveillance'' argument suffers from one
major flaw. It focuses strongly on the abilities of and dangers posed by agencies like the \ac{NSA} and ignores the
problems of local, state, and sometimes-surprisingly-cash-strapped federal law enforcement. The boom in the existence of
digital evidence is clear, but as shown, law enforcement already has trouble acquiring the evidence with the help of
tech and communications companies, and does not have the funding or capability to get it on its own \cite{carter_2018}.
Exacerbating the situation is the ``tech effect,'' which is increasing jurors' expectations of hard evidence in cases
where it may be suspected to exist \cite{shelton_study_2006}.

Still, the fact that the tools of mass surveillance are out of reach for most law enforcement must not be relied upon.
That is, most likely, a temporary situation. A safer criticism of the ``Golden Age'' framing of \ac{EA} is that \ac{EA}
without mass surveillance is conceivable. \ac{EA} implementations that enable law enforcement but thwart mass
surveillance by remote powers subvert most of the ``Golden Age'' argument. Means for \ac{EA} to do so are explored in
future argument maps.

@@

Analyzing debates in the \ac{argmap} format invites one to seriously consider the merits of opposing arguments. Part of
that consideration includes identifying and eliminating fallacious arguments. In heated, partisan debates, fallacious
arguments spread easily, and the \ac{encryption} debate has its share, shown in \myfig{fig-arg-fallacies}.

\begin{figure}[h]
  \centering\CaptionFontSize
  \includegraphics[width=\linewidth]{arguments/build/comprehensive.fallacies.pdf}
  \caption{Fallacious Arguments of the EA Debate}
  \label{fig-arg-fallacies}
\end{figure}

Let us begin with bad arguments used to attack \ac{EA}. The first is the most common: ``\ac{EA} is a bad idea because
backdoors are insecure.'' It appears on the map as a straw man argument due to the way the term ``backdoor'' is used.
``Backdoor'' is essentially technical shorthand for ``insecure hack that should never be used in production''; when it
is used as a basket term for all \ac{EA} proposals, the audience is primed to think them all stupid and helplessly
dangerous. Thus, the arguer is presenting their opponent's request for some form of \ac{EA} in the worst possible light.

Another common argument is that implementing \ac{EA}---or even researching it---moves us inexorably down a slippery
slope, where government demands will never be satisfied. This argument can be used even if one thinks judicious
hypothetical use of \ac{EA} tools would be a good thing. Going too far and too fast is certainly a danger, but it is
both cynical and fallacious to declare the permanent destruction of privacy as the inevitable end of \ac{EA} research.

It is highly tempting to declare government calls for \ac{EA} disingenuous due to hypocritical behavior in their
treatment of the issues. For example, if combatting \ac{CSAM} is a government priority, how come Congress hasn't funded
it and the Justice Department hasn't prioritized it \cite{keller_internet_2019}? This question, and others like it,
demands an answer, but it ultimately does not impact the validity (or invalidity) of pro-\ac{EA} arguments. The absence
of government funding doesn't mean technical anti-\ac{CSAM} measures are unnecessary.

The final two anti-\ac{EA} fallacies are examples of false dichotomies, presenting the situation as if there are only
two choices. \Acp{wicked-prob} have an unlimited set of possible responses, so reducing it to two (and often, presenting
one as a straw man) is misleading. One false dichotomy is that the only acceptable solutions are perfect \ac{EA} or no
\ac{EA}. This leaves no room for risk-based approaches, the typical security strategy outside the realm of cryptography.
Another false dichotomy is that regulators must either allow strong cryptography or we will live in a mass surveillance
dystopia. This one carries hints of ``slippery slope'' and appeal to emotion as well, framed as a choice between only
two futures. Framing the situation in all or nothing terms harms the chances for successful collaborative debate.

Fallacious arguments used to support \ac{EA} rely heavily on appeal to emotion. Politicians and law enforcement agents
commonly appeal to pity for child abuse victims or fear of terrorists, drug dealers, and kidnappers to make their point.
Public safety is a core value in the debate and the technical community needs to and does take these concerns seriously
\cite{schneier_scaring_2019}. These appeals become fallacious when they are used to manipulate the audience into
supporting measures incommensurate with the problems, or to manipulate the audience into thinking that tech somehow
actually does not care about these issues.

Another argument used to subvert anti-EA arguments from experts goes along the lines of, since we put a man on the moon,
we can surely create secure \ac{EA} \cite{cushing_moon_2018}. This is a weak analogy. The problem of landing an
astronaut on the moon is different from the problem of encryption and \ac{EA} in every way except that it was hard. The
Apollo program solved mostly tame problems, and it had enormous government backing. Resolving the encryption debate has
neither of these factors. Many similar technological-progress based arguments suffer the same faults.

Lastly, government officials often pose \ac{EA} as a problem that security experts simply have not researched enough. If
they just ``nerd harder,'' they can find a solution \cite{schneier_2019}. This misses the point of research done up to
this point. Encryption and \ac{EA} is a \ac{wicked-prob} for which tame, technical-only solutions will not work
\cite{rozenshtein_wicked_2018}. Even on the technical side, experts have stated time and again that depending how you
look at it, the technical problem is solved---\ac{EA} is easy from a purely cryptographic point of view. The hard part
is the security of the interfaces with the human users and administers of the system \cite{abelson_risks_1997}
\cite{abelson_2015}. This may be an area of anemic academic research, but to frame that as the primary roadblock to
progress utterly misses the point.

@@

\begin{figure}[h]
  \centering\CaptionFontSize
  \includegraphics[width=\linewidth]{arguments/build/comprehensive.measures.pdf}
  \caption{EA and its Alternatives}
  \label{fig-arg-measures}
\end{figure}

@@

\begin{figure}[h]
  \centering\CaptionFontSize
  \includegraphics[width=\linewidth]{arguments/build/comprehensive.classes.pdf}
  \caption{Classes of EA}
  \label{fig-arg-classes}
\end{figure}

@@

\begin{figure}[h]
  \centering\CaptionFontSize
  \includegraphics[width=\linewidth]{arguments/build/comprehensive.proposals.pdf}
  \caption{EA Proposals}
  \label{fig-arg-proposals}
\end{figure}
